RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-11 doc/paper.tex
Start woring on Intro

@@

\newpage
%\section*{References}
\bibliographystyle{abbrv}	
%\bibliography{bib}

>>>>

	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade to study it intensively. SR can be seen as a generalization of the well known  concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}. All regression models in principle have the same task: given a set of a $n$-dimensional input data and the output data, the aim is to find a  function consisting of $n$ (input) variables that fits to the output data w.r.t. some in advance known measure. When aiming a model to be a linear combination of input variables, it represents the problem of linear regression. However, when there are some nonlinear relations between variables, which are relevant, linear regression models are not enough. This is the point where symbolic regression comes into the play. Unlike linear regression, it allows the search over the space of all possible mathematical formulas in order to find the best fitting ones able to  predict the output variable from the input variables. The base of constructing the explicit formula are the basis operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.  \fxnote{Marko: proceed}
	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef

@@

\newpage
%\section*{References}
\bibliographystyle{abbrv}	
\bibliography{bib}
